### 2022-05-06 supplement.Rmd
Selection models

>>>>

```{r,selection_models}
# random-effects 2 level model
r_mod <- rma.uni(yi = dat$gi, vi = dat$vi)

# EASY WEIGHT_FUNCTION MODEL
# Lauer 2019 "We first implemented the Vevea and Hedges (1995) weightfunction model 
# to estimate the population effect size after adjusting for selection bias."
# specifying p value cutpoints of 0.01, 0.05, and 0.10
sel_mod=selmodel(r_mod, type='stepfun',steps=c(0.01,.05, .3, 1),verbose=TRUE)
print(sel_mod)
print('The publication_bias-corrected estimate of the meta analytic effect is  0.21')

# 4 DIFFERENT STEP FUNCTION MODELS
# Lauer 2019 "We then conducted Vevea and Woods’ (2005) selection model analyses that 
# provide estimates of the mean weighted effect size assuming varying degrees of selection bias."
tab <- data.frame(
  steps = c(0.005, 0.01, 0.05, 0.10, 0.25, 0.35, 0.50, 0.65, 0.75, 0.90, 0.95, 0.99, 0.995, 1),
  delta.mod.1 = c(1, 0.99, 0.95, 0.80, 0.75, 0.65, 0.60, 0.55, 0.50, 0.50, 0.50, 0.50, 0.50, 0.50),
  delta.sev.1 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.40, 0.35, 0.30, 0.25, 0.10, 0.10, 0.10, 0.10),
  delta.mod.2 = c(1, 0.99, 0.95, 0.90, 0.80, 0.75, 0.60, 0.60, 0.75, 0.80, 0.90, 0.95, 0.99, 1.00),
  delta.sev.2 = c(1, 0.99, 0.90, 0.75, 0.60, 0.50, 0.25, 0.25, 0.50, 0.60, 0.75, 0.90, 0.99, 1.00))

sel_moderateonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.1,verbose=TRUE)
sel_severeonetailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.1,verbose=TRUE)
sel_moderatetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.mod.2,verbose=TRUE)
sel_severetwotailed=selmodel(r_mod, type='stepfun',steps=tab$steps,delta=tab$delta.sev.2,verbose=TRUE)

print(sel_moderateonetailed)
print(sel_severeonetailed)
print(sel_moderatetwotailed)
print(sel_severetwotailed)

print('The publication_bias-corrected estimate of the meta analytic effect using a moderate one-tailed selection model is  0.1302')
print('The publication_bias-corrected estimate of the meta analytic effect using a severe one-tailed selection model is  -0.1421 ')
print('The publication_bias-corrected estimate of the meta analytic effect using a moderate two-tailed selection model is  0.2234')
print('The publication_bias-corrected estimate of the meta analytic effect using a severe two-tailed selection model is  0.1875')

interpretation="The analysis of four more selection models  showed that the effect is robustly larger than 0.1, excepting severe publication bias based on p-value"

```
